\chapter*{Acknowledgments}

This was a long journey filled with emotion, drama, and friendship. 
I wholeheartedly regret taking on this PhD. At the same time, it did expose me to research, and I loved the work. This was an unimaginably difficult time of my life, which forced me to grow at an incredible rate and come face-to-face with challenges like abuse and poverty. 
%If you are reading this and thinking about doing a PhD, I would recommend against it wholeheartedly, but I have no reason for this perception of my experience.
Still, my time with the Wearable Computer Lab was fun. Like-minded people surrounded me, and you all made me grow as a person immensely.
I already miss the freedom being surrounded by so much technology afforded me.
Despite the stress and drama that plagued me all this time.
Thanks to you, I have many positive memories and stories to tell.

First, I should thank my supervisors. I am sorry for all (well, most) of the arguments and heated debates. 
Most people would have left me once they realized that the research was not what they hoped for and that it was struggling to get out there. 
This was a hard PhD, there is no doubt about it, but I did not help it much. Still, I doubt that I should have done a PhD; I must have been quite a handful. 

Dr. Joanne Zucco, you always told me what I needed to hear, whether it was a hard truth or providing silence and listening. You are an amazingly gifted person, and I doubt I would have maintained my sanity without you.
Thank you for leaving your comfort zone to be the person I needed and staying on board the ship throughout this turbulent journey. 

Dr. Wolfgang Mayer, you always looked at things from the other angle; you found critics of my work that no one in my field, without you pushing me to do more and move further, I would not be where I am today.
I appreciate that you seem to be the person I believe you are to this day. It was an honor and privilege to have you as a supervisor.

Dr. Ross T. Smith, you must have gone through a lot for me, things that I probably never want to hear about. 
Thank you for being there when I got emotional and for listening to me complain about my reviewers every time.
Thank you for not abandoning me when I lost my temper because my research hit a dead end. 
Thank you for turning a blind eye when I was a broken human. 
Thank you for pouring so much work into me, even while you did not benefit much.
You are a great supervisor and a talented manager. I sincerely wish you the best for the rest of your career, and I hope things become more interesting for you. 

To the other people who helped me aid my research. Dr. Brandon Matthews, Thank you for being the intermediary between Ross and me and for talking me through some of the most technical conversations I may ever get to have. I would also like to extend a thank you to Dr. Adam Drogemuller. You helped me grow my understanding of data visualization experiences and helped me become a better data analyst. 

To everyone with whom I was lucky enough to experience my Ph.D., thank you for being there and for being good people (for the most part). 
Thank you for helping me when I needed it, letting me stir you up, and not telling me off for distracting you and having interesting problems. 
You all made my PHD worthwhile and eventful, and the stories we have made I will keep telling to people for the rest of my life.

I would also like to thank the staff of UNISA (now the University of Adelaide) for making me a stronger person by constantly presenting me with challenges that I had to overcome at some of the most difficult times. 
Regardless of my health, be it from cancer, depression, or heart conditions, you maintained your dedicated focus on this task.
Your efforts took me from a good manager to an excellent one as I learned how to fix the issues you manufactured in a subtle manner. 
After working with you all, I do not think there is any problem I can not handle. 

I would also like to thank Dr. Ameliorate and Bradly Ross Richards for providing me with your artwork for this thesis.
My friends (you know who you are) for putting up with me being broke, time-poor, and miserable for years on end (I am surprised you hang around).
I want to thank my employers over these years during this Ph.D who allowed me to keep my house, Dr. Michael Ulpen from Sabit University, and everyone One Forty One, especially my employer, Dr. Jan Rombouts, for allowing me to keep a roof over my head and understanding when I was being put in a difficult position.
And a special thanks to the team at Siemens Healthineers for teaching me the skills I needed to know for this Ph.D.

Finally, thank you to my family. I want to thank my mum (Kylie Dunstan) for housing me when I returned to the country during the COVID-19 pandemic and could not find a suitable place to rent. Also, my sister (Paige Wijeratne), along with my Mum, listened to me stress out and lose my hair over having no money and being harassed on all sides of my life. It must have been hard having to experience that. 
%I also want to thank my partner (Nguyễn Hà Châu) and her mother (Hà Thị Duy Trà) for feeding me and caring for me while I was busy writing my thesis and making sure that I left my computer at least once a month and not only ate food but ate healthily. This thesis would have harmed me more if not for your efforts. 
I also want to thank my partner (Nguyen Ha Chau) and her mother (Ha Thi Duy Tra) for feeding me and caring for me while I was busy writing my thesis and making sure that I left my computer at least once a month and not only ate food but ate healthily. This thesis would have harmed me more if not for your efforts. 

This research was supported by an Australian Government Research Training Program (RTP) Scholarship.

